Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors

### 2018-08-01 main.tex
Howards updates

\subsection{Numerical Tests}\label{sec:numerical-tests}
Consider the differences of the left- and right-hand side of equation~\eqref{eq:branch-cut-near}
\begin{equation}\label{eq:difference}
D(z) := U(0,z) - \sqrt{\frac{z}{2\cpi}} K_{\frac{1}{4}}\left(\frac{1}{4}z^2\right).
\end{equation}
Table~\ref{tab:computations-for-difference} presents four computations for $D(z)$, one value for each quadrant in the complex plane.
\begin{table}[ht]
\centering
\begin{tabular}{rcc}
	\hline
	$z\ \ $ & & $D(z)$\\
	\hline
	\tableRowSpace{} $1+\iunit$ & & $2 \cdot 10^{-10} - 2 \cdot 10^{-10} \iunit$\\
	$-1+\iunit$& & $2.222121916 - 1.116719816 \iunit$\\
	$-1-\iunit$& & $2.222121916 + 1.116719816 \iunit$\\
	$1-\iunit$ & & $2 \cdot 10^{-10} + 2 \cdot 10^{-10} \iunit$\\
	\hline
\end{tabular}
\caption{Four computations of $D(z)$ in \Maple.}
\label{tab:computations-for-difference}
\end{table}

>>>>

\subsection{Numerical Tests}\label{sec:numerical-tests}
Consider the difference of the left- and right-hand sides of equation~\eqref{eq:branch-cut-near}, namely
\begin{equation}\label{eq:difference}
D(z) := U(0,z) - \sqrt{\frac{z}{2\cpi}} K_{\frac{1}{4}}\left(\frac{1}{4}z^2\right).
\end{equation}
Table~\ref{tab:computations-for-difference} presents four numerical evaluations for $D(z)$, one value for each quadrant in the complex plane.
\begin{table}[ht]
\centering
\begin{tabular}{rcc}
	\hline
	$z\ \ $ & & $D(z)$\\
	\hline
	\tableRowSpace{} $1+\iunit$ & & $2 \cdot 10^{-10} - 2 \cdot 10^{-10} \iunit$\\
	$-1+\iunit$& & $2.222121916 - 1.116719816 \iunit$\\
	$-1-\iunit$& & $2.222121916 + 1.116719816 \iunit$\\
	$1-\iunit$ & & $2 \cdot 10^{-10} + 2 \cdot 10^{-10} \iunit$\\
	\hline
\end{tabular}
\caption{Four numerical evaluations of $D(z)$ in \Maple.}
\label{tab:computations-for-difference}
\end{table}
